---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# DeepOperators

The goal of DeepOperators is to provide pre-trained deeply learned boolean operators.

The `deep_and` and `deep_or` operators turn plain old business logic into "deep learning", "machine learning", and "AI" problems. Because business folk sometimes dictate how problems are solved, DeepOperators enables the ~~programmer~~ Data Scientist to use "deep learning" when it is required but it would otherwise be more practical to use built-in logical operators.

## Installation

You can install the development version of DeepOperators from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("ellisvalentiner/DeepOperators")
```

## Example

This is a basic example of the DeepOperator functions:

```{r}
library(DeepOperators)
deep_and(TRUE, FALSE)
deep_and(TRUE, TRUE)
deep_or(TRUE, FALSE)
deep_or(FALSE, FALSE)
```

Additionally DeepOperator provides function to automatically re-train the `deep_and` and `deep_or` operators.

```{r, eval=FALSE}
train_deep_or()
train_deep_and()
```

## Provenance

This package was inspired by [Fizz Buzz in Tensorflow](http://joelgrus.com/2016/05/23/fizz-buzz-in-tensorflow/).
